Proof No Diamond (3 layers)

### 2023-10-10 Yuke No Diamond for 3 layers.tex
proof

\documentclass[]{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\ReLU}{\mathrm{ReLU}}

@@

@@

@@

We proceed inductively, and prove the inductive step.
The initialization is obvious as DeepPoly is always exact for the initialization layer.

\begin{lemma}
	Let $L,L'$ two consecutive layers.
	Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by DeepPoly equals to the exact lower and upper bounds of $m$.

	Then DeepPoly computes the exact lower and upper bounds for every node $n$ of layer $L'$.
\end{lemma}

	Deeppoly computes its upper bound using $m=\sum_{n}w(mn)\hat{n}+b,$ by taking all $n$ that $w(mn)>0$ to upper bound and taking all $n$ that $w(mn)<0$ to lower bound.

	On the other hand, by assumption, for all $n$ that $S(n)\neq 0$(which is equivalent to $w(mn)\neq 0$), the upper and lower bounds stored by Interval Arithmetic is equal to their exact upper and lower bounds, i.e., their maximal and minimal values. And for every $n$, its upper bound if $w(mn)>0$ or lower bound if $w(mn)<0$ is equal to the maximal value of $n^s$.

	Hence $$u(m)_{IA}=\sum_{n}w(mn)\ReLU(\max(n^s))+b=\max(m^s).$$ This is what we want to show.
\end{proof}

Use Lemma 3, we can see the Interval Arithmetic upper and lower bounds of the output node $z$ are equal to the actual upper and lower bounds of $z$

>>>>

\documentclass[]{article}
\usepackage{amsmath, amsthm, amssymb, amsfonts}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}
\theoremstyle{definition}
\newtheorem{definition}{Definition}
\newcommand{\ReLU}{\mathrm{ReLU}}

@@

As direct corrolary of Lemma \ref{lemma2}, we obtain:

\begin{corollary}
	\label{cor1}
	$$\max(n^-)=\sum_{m \in L, w(m n)>0}w(m n) \max(m^+) + \sum_{m \in L, w(m n)<0}w(m n) \min(m^+) + bias_n$$
	$$\min(n^-)=\sum_{m \in L, w(m n)>0}w(m n) \min(m^+) + \sum_{m \in L, w(m n)<0}w(m n) \max(m^+) + bias_n$$
\end{corollary}

@@

To prove that DeepPoly bounds are the same as the exact bounds computed above, 
we show that even the box abstraction (which is easier) would reach the exact bounds.
We proceed inductively, and prove the inductive step.
The initialization is obvious as Box Abstraction/DeepPoly is always exact for the initialization layer.

\begin{lemma}
	Let $L,L'$ be two consecutive layers.
	Assume for all node $m$ of $L$ that the lower and upper bounds for $m$ used by box abstraction equals to the exact lower and upper bounds of $m$ (as expressed above), i.e.
	$\bar{f}(m)=max(m)$ and $\underline{f}(m)=min(m)$.

	Then Box abstraction computes the exact lower and upper bounds for every node $n$ of layer $L'$, ie $\bar{f}(n)=max(n)$ and $\underline{f}(n)=min(n)$.
\end{lemma}

	The Box absraction computes its upper bound using:
	$$\bar{f}(n^-)= \sum_{w(mn)>0} w(mn) \bar{f}(m^+) + \sum_{w(mn)<0} w(mn) \underline{f}(m^+) + bias_n$$

	By induction hypothesis, we have 
	$\bar{f}(m^+)=max(m^+)$ and
	$\underline{f}(m^+)=min(m^+)$, thus 
	applying Corollary \ref{cor1}, we obtain
	$\bar{f}(n^-)=max(n^-)$ and 
	$\underline{f}(n^-)=min(n^-)$.

	Now, if $\underline{f}(n^-)=min(n^-)<0$, 
	then $\underline{f}(n^+)=min(n^+)=0$, 
	and otherwise 
	$\underline{f}(n^+)=min(n^+)=\underline{f}(n^-)=min(n^-)$.

\end{proof}

@@
